---
title: "gpelose_OriginalHomeworkCode_03"
author: "Greg Pelose"
date: "10/9/2019"
output: html_document
---
***
```{r}
install.packages("curl")
install.packages("ggplot2")
install.packages("gridextra")
install.packages("manipulate")
install.packages("lmodel2")
```

```{r}
library("curl")
library("ggplot2")
library("manipulate")
library("lmodel2")
```

I will first be uploading the zombies.cvs data using the curl cuntion and assigning this the varable "f"

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

FIRST QUESTION:
(reminder to add line)
Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples.

```{r}
#Ask for the names of the categories 
names(d)
```

```{r}
# Ask for summaries of the data 
summary(d)
```

This above only gives the sample mean I need to find th population mean.  

```{r}
table(height)
```

Finding the populaiton mean and standard deviation for height!

```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v)}
sd_height <- pop_sd(x)
sd_height
```


```{r}
summary(d)
```

```{r}
table(weight)
```
Finding the pop mean and sd for weight
```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight

```







I will now plot the data







