---
title: "gpelose_FinalHomeworkCode_03"
author: "Greg Pelose"
date: "10/11/2019"
output: html_document
---

title: "gpelose_OriginalHomeworkCode_03"
author: "Greg Pelose"
date: "10/9/2019"
output: html_document
---
***
```{r}
install.packages("curl")
install.packages("ggplot2")
install.packages("gridextra")
install.packages("manipulate")
install.packages("lmodel2")
```

```{r}
library("curl")
library("ggplot2")
library("manipulate")
library("lmodel2")
```

I will first be uploading the zombies.cvs data using the curl cuntion and assigning this the varable "f"

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

FIRST QUESTION:
***
Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples.

```{r}
#Ask for the names of the categories 
names(d)
```

```{r}
# Ask for summaries of the data 
summary(d)
```


```{r}
table(height)
```

Finding the populaiton mean and standard deviation for height!
***
```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v_height)}
sd_height <- pop_sd(x)
sd_height
```

Finding the pop mean and sd for weight

```{r}
table(d$weight)
weight <- (d$weight)
```

```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight

```

Finding the pop mean and sd for age

```{r}
age <- (d$age)

age_mean <- function(x){sum(age)/1000}
mu_age <- age_mean(x)
mu_age

pop_v <- function(x){sum((age-mu_age)^2)/(1000)}
v_age <- pop_v(x)
v_age

pop_sd <- function(x){sqrt(v_age)}
sd_age <- pop_sd(x)
sd_age

```

Finding the pop mean and sd for number of zombies killed

```{r}
z_killed <- (d$zombies_killed)

z_killed_mean <- function(x){sum(z_killed)/1000}
mu_z_killed <- z_killed_mean(x)
mu_z_killed

pop_v <- function(x){sum((z_killed-mu_z_killed)^2)/(1000)}
v_z_killed <- pop_v(x)
v_z_killed

pop_sd <- function(x){sqrt(v_z_killed)}
sd_z_killed <- pop_sd(x)
sd_z_killed
```

Finding the pop mean and sd for years_of_education

```{r}
y_of_edu <- (d$years_of_education)

y_of_edu_mean <- function(x){sum(y_of_edu)/1000}
mu_y_of_edu <- y_of_edu_mean(x)
mu_y_of_edu

pop_v <- function(x){sum((y_of_edu-mu_y_of_edu)^2)/(1000)}
v_y_of_edu <- pop_v(x)
v_y_of_edu

pop_sd <- function(x){sqrt(v_y_of_edu)}
sd_y_of_edu <- pop_sd(x)
sd_y_of_edu
```


QUESTION 2:
Use {ggplot} to make boxplots of each of these variables by gender.(height, weight, age, number of zombies killed, and years of education)

Boxplot for gender and height.
```{r}
f <- ggplot(data=d, aes(x=gender, y=height))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for gender and weight.

```{r}
f <- ggplot(data=d, aes(x=gender, y=weight))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for age.

```{r}
f <- ggplot(data=d, aes(x=gender, y=age))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for zombies_killed.

```{r}
f <- ggplot(data=d, aes(x=gender, y=zombies_killed))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for years of education:

```{r}
f <- ggplot(data=d, aes(x=gender, y=years_of_education))
g <- f + geom_boxplot(color="blue") #i like blue
g
```

QUESTION #3
Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?

height vs age, red color becasue we are talking about zombies. 
```{r}
f <- ggplot(data=d, aes(x=height, y=age))
g <- f + geom_point(color="red")
g
```

weight vs age, orange becasue we are close to halloween 

```{r}
f <- ggplot(data=d, aes(x=weight, y=age))
g <- f + geom_point(color="orange")
g
```

Written response:

height and age is definitely more related than weight and age. As the people get older they also seem to generally get taller. There seems like there is a slight trend in weight and age, where as you get older you get heavier, but it is not as pronounced as height vs age. There is definitley more variance in weight and age. 

Question #4:

Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn?

So I will be using my mean and sd that I obtained from earlier to plug into some rnorm histograms. This will allow for me to put my information into a normal distribution.

Starting with height.

```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v_height)}
sd_height <- pop_sd(x)
sd_height
```

```{r}
n <- 1000
v <- rnorm(n,mu,sd_height)
hist(v)
qqnorm(v)
qqline(v)
```
Yes the distribution for height looks to be normal. 

now I will do weight

```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight
```

```{r}
n <- 1000
v <- rnorm(n,mu_weight,sd_weight)
hist(v)
qqnorm(v)
qqline(v)
```

The distribution for weight also seems to look very normal as well.

Now I will do age.

```{r}
age <- (d$age)

age_mean <- function(x){sum(age)/1000}
mu_age <- age_mean(x)
mu_age

pop_v <- function(x){sum((age-mu_age)^2)/(1000)}
v_age <- pop_v(x)
v_age

pop_sd <- function(x){sqrt(v_age)}
sd_age <- pop_sd(x)
sd_age
```

```{r}
n <- 1000
v <- rnorm(n,mu_age,sd_age)
hist(v)
qqnorm(v)
qqline(v)
```
this also looks to be quite normal as nothing deviates from the line too much. 

```{r}
z_killed <- (d$zombies_killed)

z_killed_mean <- function(x){sum(z_killed)/1000}
mu_z_killed <- z_killed_mean(x)
mu_z_killed

pop_v <- function(x){sum((z_killed-mu_z_killed)^2)/(1000)}
v_z_killed <- pop_v(x)
v_z_killed

pop_sd <- function(x){sqrt(v_z_killed)}
sd_z_killed <- pop_sd(x)
sd_z_killed
```

```{r}
n <- 1000
v <- rnorm(n,mu_z_killed,sd_z_killed)
hist(v)
qqnorm(v)
library(car)
qqPlot(v)
qqline(v)
```

for number of zombies killed. I found this distrubtion to not fit the normal curve. I added qqplot and qqline to investigate this a bit more and some of the dots fall slightly outside of the boundaries. Due to this, one could state that the number of zombies killed is skewed to the right.


I will next do years of edu

```{r}
y_of_edu <- (d$years_of_education)

y_of_edu_mean <- function(x){sum(y_of_edu)/1000}
mu_y_of_edu <- y_of_edu_mean(x)
mu_y_of_edu

pop_v <- function(x){sum((y_of_edu-mu_y_of_edu)^2)/(1000)}
v_y_of_edu <- pop_v(x)
v_y_of_edu

pop_sd <- function(x){sqrt(v_y_of_edu)}
sd_y_of_edu <- pop_sd(x)
sd_y_of_edu
```

```{r}
n <- 1000
v <- rnorm(n,mu_y_of_edu,sd_y_of_edu)
hist(v)
qqnorm(v)
qqline(v)
```

I would say that the years of education look to have a normal distribution as well. The data all falls very close to the normal line. There are a few data points that are a bit skewed on each end but not enough for me to say that this data is not normal. 


Question#5

Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal...


```{r}
mysample <- d[sample(1:nrow(d), 30,
   replace=FALSE),]
mysample
```

height calculations for my n=30 sample.
***
```{r}
table(mysample$height)
```

```{r}
m_h <- mean(mysample$height)
sd_h <- sd(mysample$height)
m_h
sd_h
```

```{r}
h_pop_se <- sqrt(18.55861^2/30)
h_pop_se
```

```{r}
lower <- m_h - qnorm(1 - 0.05/2) * h_pop_se 
upper <- m_h + qnorm(1 - 0.05/2) * h_pop_se 
ci <- c(lower, upper)
ci
```

weight calculations of n=30 sample.
***
```{r}
m_w <- mean(mysample$weight)
sd_w <-sd(mysample$weight)
m_w
sd_w
```
```{r}
pop_se <- sqrt(18.39186^2/30)
pop_se
```

```{r}
lower <- m_w - qnorm(1 - 0.05/2) * pop_se 
upper <- m_w + qnorm(1 - 0.05/2) * pop_se 
ci <- c(lower, upper)
ci
```

age calculations of my n=30 sample
***
```{r}
m_age <- mean(mysample$age)
sd_age <-sd(mysample$age)
m_age
sd_age
```
```{r}
age_pop_se <- sqrt(2.963583^2/30)
age_pop_se
```

```{r}
lower <- m_age - qnorm(1 - 0.05/2) * age_pop_se 
upper <- m_age + qnorm(1 - 0.05/2) * age_pop_se 
ci <- c(lower, upper)
ci
```

z_killed calculations of my n=30 sample
***
```{r}
m_z_killed <- mean(mysample$zombies_killed)
sd_z_killed <- sd(mysample$zombies_killed)
m_z_killed
sd_z_killed
```
```{r}
z_killed_pop_se <- sqrt(1.747551^2/30)
z_killed_pop_se
```

```{r}
lower <- m_age - qnorm(1 - 0.05/2) * z_killed_pop_se 
upper <- m_age + qnorm(1 - 0.05/2) * z_killed_pop_se 
ci <- c(lower, upper)
ci
```

last one, y_of_edu calculations of my n=30 sample 
***
```{r}
m_y_of_edu <- mean(mysample$years_of_education)
sd_y_of_edu <- sd(mysample$years_of_education)
m_y_of_edu
sd_y_of_edu
```
```{r}
y_of_edu_pop_se <- sqrt(1.675704^2/30)
y_of_edu_pop_se
```

```{r}
lower <- m_age - qnorm(1 - 0.05/2) * z_killed_pop_se 
upper <- m_age + qnorm(1 - 0.05/2) * z_killed_pop_se 
ci <- c(lower, upper)
ci
```

Question #6

Now draw 99 more random samples of 30 zombie apocalypse survivors, and calculate the mean for each variable for each of these samples. Together with the first sample you drew, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution of means for each variable? How do the standard deviations of means compare to the standard errors estimated in [5]? What do these sampling distributions look like (a graph might help here)? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution?

```{r}
install.packages("tidyverse")
install.packages("dplyr")
```

```{r}
library("tidyverse")
library("dplyr")
```


```{r}
k <- 100
n <- 30
s <- NULL

for (i in 1:k){
    s[[i]] <- sample(d$height,size=n, replace=TRUE)
}
s
```
IN CLASS:
```{r}
k <- 100
n <- 30
s <- NULL

for (i in 1:k){
    s[[i]] <- sample_n(d,size=n, replace=FALSE)#so we are using the sample_n from the dplyr package because it allows for us to just take the analysis from my entire action.
}
s
#also replace should alw
```


```{r}
m_height <- NULL
for (i in 1:k){
  m_height[i] <- mean(d[[i]]$height)
}
mean(m_height)
#need to double check this action. 
```

I was able to select all 99 samples, I am still struggling to get the mean and sd of all of the samples 
```{r}
table(s$height)
```
```{r}
summary(s)
```

this was the mean that I got 67.56, I will not find the standard deviation 

```{r}
sd(s)
```

I am unable to find the standard deviations of each variable individually from my massive sample. 
