---
title: "gpelose_OriginalHomeworkCode_03"
author: "Greg Pelose"
date: "10/9/2019"
output: html_document
---
***
```{r}
install.packages("curl")
install.packages("ggplot2")
install.packages("gridextra")
install.packages("manipulate")
install.packages("lmodel2")
```

```{r}
library("curl")
library("ggplot2")
library("manipulate")
library("lmodel2")
```

I will first be uploading the zombies.cvs data using the curl cuntion and assigning this the varable "f"

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

FIRST QUESTION:
(reminder to add line)
Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples.

```{r}
#Ask for the names of the categories 
names(d)
```

```{r}
# Ask for summaries of the data 
summary(d)
```

This above only gives the sample mean I need to find th population mean.  

```{r}
table(height)
```

Finding the populaiton mean and standard deviation for height!

```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v)}
sd_height <- pop_sd(x)
sd_height
```


```{r}
summary(d)
```

Finding the population mean and sd for weight. (it took me over an hour to realize that i need d$weight instead of just weight, for some reason I do not need the $ for height when doing my first sample)
```{r}
table(d$weight)
weight <- (d$weight)
```


Finding the pop mean and sd for weight
```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight

```

Finding the pop mean and sd for age

```{r}
age <- (d$age)

age_mean <- function(x){sum(age)/1000}
mu_age <- age_mean(x)
mu_age

pop_v <- function(x){sum((age-mu_age)^2)/(1000)}
v_age <- pop_v(x)
v_age

pop_sd <- function(x){sqrt(v_age)}
sd_age <- pop_sd(x)
sd_age

```

Finding the pop mean and sd for number of zombies killed

```{r}
z_killed <- (d$zombies_killed)

z_killed_mean <- function(x){sum(z_killed)/1000}
mu_z_killed <- z_killed_mean(x)
mu_z_killed

pop_v <- function(x){sum((z_killed-mu_z_killed)^2)/(1000)}
v_z_killed <- pop_v(x)
v_z_killed

pop_sd <- function(x){sqrt(v_z_killed)}
sd_z_killed <- pop_sd(x)
sd_z_killed
```

Finding the pop mean and sd for years_of_education

```{r}
y_of_edu <- (d$years_of_education)

y_of_edu_mean <- function(x){sum(y_of_edu)/1000}
mu_y_of_edu <- y_of_edu_mean(x)
mu_y_of_edu

pop_v <- function(x){sum((y_of_edu-mu_y_of_edu)^2)/(1000)}
v_y_of_edu <- pop_v(x)
v_y_of_edu

pop_sd <- function(x){sqrt(v_y_of_edu)}
sd_y_of_edu <- pop_sd(x)
sd_y_of_edu
```


QUESTION 2:
Use {ggplot} to make boxplots of each of these variables by gender.(height, weight, age, number of zombies killed, and years of education)

Boxplot for gender and height.
```{r}
f <- ggplot(data=d, aes(x=gender, y=height))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for gender and weight.

```{r}
f <- ggplot(data=d, aes(x=gender, y=weight))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for age.

```{r}
f <- ggplot(data=d, aes(x=gender, y=age))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for zombies_killed.

```{r}
f <- ggplot(data=d, aes(x=gender, y=zombies_killed))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for years of education:

```{r}
f <- ggplot(data=d, aes(x=gender, y=years_of_education))
g <- f + geom_boxplot(color="blue")
g
```

QUESTION #3
Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?

```{r}

```





