---
title: "gpelose_OriginalHomeworkCode_03"
author: "Greg Pelose"
date: "10/9/2019"
output: html_document
---
***
## Comments from Laura B-W are at the bottom, underneath each of the five challenges faced.


```{r}
library("curl")
library("ggplot2")
library("manipulate")
library("lmodel2")
```

I will first be uploading the zombies.cvs data using the curl funtion and assigning this the varable "f"

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

FIRST QUESTION:
(reminder to add line)
Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples.

```{r}
#Ask for the names of the categories 
names(d)
```

```{r}
# Ask for summaries of the data 
summary(d)
```

This above only gives the sample mean I need to find th population mean.  

```{r}
height <- table(d$height)
head(height)
```

Finding the populaiton mean and standard deviation for height!

```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v)}
sd_height <- pop_sd(x)
sd_height
```


```{r}
summary(d)
```

Finding the population mean and sd for weight. (it took me over an hour to realize that i need d$weight instead of just weight, for some reason I do not need the $ for height when doing my first sample)
```{r}
table(d$weight)
weight <- (d$weight)
```


Finding the pop mean and sd for weight
```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight

```

Finding the pop mean and sd for age

```{r}
age <- (d$age)

age_mean <- function(x){sum(age)/1000}
mu_age <- age_mean(x)
mu_age

pop_v <- function(x){sum((age-mu_age)^2)/(1000)}
v_age <- pop_v(x)
v_age

pop_sd <- function(x){sqrt(v_age)}
sd_age <- pop_sd(x)
sd_age

```

Finding the pop mean and sd for number of zombies killed

```{r}
z_killed <- (d$zombies_killed)

z_killed_mean <- function(x){sum(z_killed)/1000}
mu_z_killed <- z_killed_mean(x)
mu_z_killed

pop_v <- function(x){sum((z_killed-mu_z_killed)^2)/(1000)}
v_z_killed <- pop_v(x)
v_z_killed

pop_sd <- function(x){sqrt(v_z_killed)}
sd_z_killed <- pop_sd(x)
sd_z_killed
```

Finding the pop mean and sd for years_of_education

```{r}
y_of_edu <- (d$years_of_education)

y_of_edu_mean <- function(x){sum(y_of_edu)/1000}
mu_y_of_edu <- y_of_edu_mean(x)
mu_y_of_edu

pop_v <- function(x){sum((y_of_edu-mu_y_of_edu)^2)/(1000)}
v_y_of_edu <- pop_v(x)
v_y_of_edu

pop_sd <- function(x){sqrt(v_y_of_edu)}
sd_y_of_edu <- pop_sd(x)
sd_y_of_edu
```


QUESTION 2:
Use {ggplot} to make boxplots of each of these variables by gender.(height, weight, age, number of zombies killed, and years of education)

Boxplot for gender and height.
```{r}
f <- ggplot(data=d, aes(x=gender, y=height))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for gender and weight.

```{r}
f <- ggplot(data=d, aes(x=gender, y=weight))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for age.

```{r}
f <- ggplot(data=d, aes(x=gender, y=age))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for zombies_killed.

```{r}
f <- ggplot(data=d, aes(x=gender, y=zombies_killed))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for years of education:

```{r}
f <- ggplot(data=d, aes(x=gender, y=years_of_education))
g <- f + geom_boxplot(color="blue")
g
```

QUESTION #3
Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?

height vs age, red color becasue we are talking about zombies. 
```{r}
f <- ggplot(data=d, aes(x=height, y=age))
g <- f + geom_point(color="red")
g
```

weight vs age, orange becasue we are close to halloween 

```{r}
f <- ggplot(data=d, aes(x=weight, y=age))
g <- f + geom_point(color="orange")
g
```

Written response:

height and age is definitely more related than weight and age. As the people get older you seem to generally get taller. There seems like there is a slight trend in weight and age, where as you get older you get heavier, but it is not a pronounced as height vs age. There is definitley more variance in weight and age. 

Question #4:

Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn?

So I will be using my mean and sd that I obtained from earlier to plug into some rnorm histograms. This will allow for me to put my information into a normal distribution.

Starting with height.

```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v)}
sd_height <- pop_sd(x)
sd_height
```

```{r}
n <- 1000
v <- rnorm(n,mu,sd_height)
hist(v)
qqnorm(v)
qqline(v)
```
Yes the distribution for height looks to be quite normal. 

now I will do weight

```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight
```

```{r}
n <- 1000
v <- rnorm(n,mu_weight,sd_weight)
hist(v)
qqnorm(v)
qqline(v)
```

The distribution for weight also seems to look very normal as well.

Now I will do age.

```{r}
age <- (d$age)

age_mean <- function(x){sum(age)/1000}
mu_age <- age_mean(x)
mu_age

pop_v <- function(x){sum((age-mu_age)^2)/(1000)}
v_age <- pop_v(x)
v_age

pop_sd <- function(x){sqrt(v_age)}
sd_age <- pop_sd(x)
sd_age
```

```{r}
n <- 1000
v <- rnorm(n,mu_age,sd_age)
hist(v)
qqnorm(v)
qqline(v)
```
this also looks to be quite normal as nothing deviates from the line too much. 

```{r}
z_killed <- (d$zombies_killed)

z_killed_mean <- function(x){sum(z_killed)/1000}
mu_z_killed <- z_killed_mean(x)
mu_z_killed

pop_v <- function(x){sum((z_killed-mu_z_killed)^2)/(1000)}
v_z_killed <- pop_v(x)
v_z_killed

pop_sd <- function(x){sqrt(v_z_killed)}
sd_z_killed <- pop_sd(x)
sd_z_killed
```

```{r}
n <- 1000
v <- rnorm(n,mu_z_killed,sd_z_killed)
hist(v)
qqnorm(v)
qqline(v)
```

I will next do years of edu

```{r}
y_of_edu <- (d$years_of_education)

y_of_edu_mean <- function(x){sum(y_of_edu)/1000}
mu_y_of_edu <- y_of_edu_mean(x)
mu_y_of_edu

pop_v <- function(x){sum((y_of_edu-mu_y_of_edu)^2)/(1000)}
v_y_of_edu <- pop_v(x)
v_y_of_edu

pop_sd <- function(x){sqrt(v_y_of_edu)}
sd_y_of_edu <- pop_sd(x)
sd_y_of_edu
```

```{r}
n <- 1000
v <- rnorm(n,mu_y_of_edu,sd_y_of_edu)
hist(v)
qqnorm(v)
qqline(v)
```

I cannot find which one of these is not drawn from a normal distribution all of them seemed to be drawn from a normal distribution if I have done this correctly?

Question#5

Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal...

```{r}
k <- 1
n <- 30
s <- NULL

for (i in 1:k){
    s[[i]] <- sample(d,size=n, replace=FALSE)
}
```

the above did not work...

```{r}
mysample <- d[sample(1:nrow(d), 30,
   replace=FALSE),]
mysample
```

```{r}
table(mysample$height)
```

```{r}
mean(mysample$height)
sd(mysample$height)
```

Constucting the standard error for my sample height.

```{r}
pop_se <- sqrt(^2/n)
```

I am struggling to figure out how to do this, I have spent a long time on number 5 and cannot figure it out, I need some help. Something happened to my stnadard deviation from my population once I have removed the 30 variables and now I can not figure out what to do and I have run out of time. 


5 Problems:

1. The biggest problem that I had was missing little parts of the code that were simple but very important. specifically I had trouble with the $ function, it worked for some portions of my code and was not needed for others which was confusing to me.

**This was also an issue I had, especially as some functions require you to do this, others require quotation marks, and other still require neither. I think it is a part of something we just have to learn by doing it? I only realized the $ was needed after looking back at old modules with similar types fo questions.**

2. I struggled with finding the sample standard error. This took up so much of my time and I could not figure out how to make it work when I should have just moved on and came back to it with fresh eyes.

**I know for sample standard error, you should just be able to use the sd() function? I was having some issues as well while I was setting it up though, but finally got it if you want to take a look at my code?**

3. Using the function "ggplot"" correctly, the formatting was different and I struggled to figure this out at first. 

**Yes! I always forget that the point of these packages is to streamline things. I kept thinking there was more I would need to put in, for example, to make a boxplot. But then I realized with ggplot, if I told it to make a boxplot, it already has built-in functionality as far as how to then use the data to calculate the size of the boxes, etc.**

4. The organization of my code is not good right now, I need to try and organize/condense everything over the weekend.

**I was able to follow it fine, though there were a few lines that kept giving me errors that I think were working for you. I also liked where you purposely kept in things that you tried and that did not work. I think I will include this for myself in the future, as this really showed me how your train of thought was working and helped me see the same kinds of problems we were coming up against. This could be useful if looking back at this in the future as a reference for other prohects.**

5. In question number 4, I was unable to find which set of data did not follow the normal distribution and thus could not properly answer the last part of #4. 

**It looks like this was something that tripped all of us up! I am guessing Dr. Schmitt will go over it in class, or we can ask, to make sure this is clearer and to find out how we can tell this from just looking at the data, or if there are specific tests we need or can run.**

**Overall, great job! I know this one took a lot of time and it looks like you learned a lot!**
