---
title: "gpelose_OriginalHomeworkCode_03"
author: "Greg Pelose"
date: "10/9/2019"
output: html_document
---
***
```{r}
install.packages("curl")
install.packages("ggplot2")
install.packages("gridextra")
install.packages("manipulate")
install.packages("lmodel2")
```

```{r}
library("curl")
library("ggplot2")
library("manipulate")
library("lmodel2")
```

I will first be uploading the zombies.cvs data using the curl cuntion and assigning this the varable "f"

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

FIRST QUESTION:
(reminder to add line)
Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples.

```{r}
#Ask for the names of the categories 
names(d)
```

```{r}
# Ask for summaries of the data 
summary(d)
```

This above only gives the sample mean I need to find th population mean.  

```{r}
table(height)
```

Finding the populaiton mean and standard deviation for height!

```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v)}
sd_height <- pop_sd(x)
sd_height
```


```{r}
summary(d)
```

Finding the population mean and sd for weight. (it took me over an hour to realize that i need d$weight instead of just weight, for some reason I do not need the $ for height when doing my first sample)
```{r}
table(d$weight)
weight <- (d$weight)
```


Finding the pop mean and sd for weight
```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight

```

Finding the pop mean and sd for age

```{r}
age <- (d$age)

age_mean <- function(x){sum(age)/1000}
mu_age <- age_mean(x)
mu_age

pop_v <- function(x){sum((age-mu_age)^2)/(1000)}
v_age <- pop_v(x)
v_age

pop_sd <- function(x){sqrt(v_age)}
sd_age <- pop_sd(x)
sd_age

```

Finding the pop mean and sd for number of zombies killed

```{r}
z_killed <- (d$zombies_killed)

z_killed_mean <- function(x){sum(z_killed)/1000}
mu_z_killed <- z_killed_mean(x)
mu_z_killed

pop_v <- function(x){sum((z_killed-mu_z_killed)^2)/(1000)}
v_z_killed <- pop_v(x)
v_z_killed

pop_sd <- function(x){sqrt(v_z_killed)}
sd_z_killed <- pop_sd(x)
sd_z_killed
```

Finding the pop mean and sd for years_of_education

```{r}
y_of_edu <- (d$years_of_education)

y_of_edu_mean <- function(x){sum(y_of_edu)/1000}
mu_y_of_edu <- y_of_edu_mean(x)
mu_y_of_edu

pop_v <- function(x){sum((y_of_edu-mu_y_of_edu)^2)/(1000)}
v_y_of_edu <- pop_v(x)
v_y_of_edu

pop_sd <- function(x){sqrt(v_y_of_edu)}
sd_y_of_edu <- pop_sd(x)
sd_y_of_edu
```


QUESTION 2:
Use {ggplot} to make boxplots of each of these variables by gender.(height, weight, age, number of zombies killed, and years of education)

Boxplot for gender and height.
```{r}
f <- ggplot(data=d, aes(x=gender, y=height))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for gender and weight.

```{r}
f <- ggplot(data=d, aes(x=gender, y=weight))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for age.

```{r}
f <- ggplot(data=d, aes(x=gender, y=age))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for zombies_killed.

```{r}
f <- ggplot(data=d, aes(x=gender, y=zombies_killed))
g <- f + geom_boxplot(color="blue")
g
```

boxplot for years of education:

```{r}
f <- ggplot(data=d, aes(x=gender, y=years_of_education))
g <- f + geom_boxplot(color="blue")
g
```

QUESTION #3
Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?

height vs age, red color becasue we are talking about zombies. 
```{r}
f <- ggplot(data=d, aes(x=height, y=age))
g <- f + geom_point(color="red")
g
```

weight vs age, orange becasue we are close to halloween 

```{r}
f <- ggplot(data=d, aes(x=weight, y=age))
g <- f + geom_point(color="orange")
g
```

Written response:

height and age is definitely more related than weight and age. As the people get older you seem to generally get taller. There seems like there is a slight trend in weight and age, where as you get older you get heavier, but it is not a pronounced as height vs age. There is definitley more variance in weight and age. 

Question #4:

Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn?

So I will be using my mean and sd that I obtained from earlier to plug into some rnorm histograms. This will allow for me to put my information into a normal distribution.

Starting with height.

```{r}
height_mean <- function(x){sum(height)/1000}
mu <- height_mean(x)
mu

pop_v <- function(x){sum((height-mu)^2)/(1000)}
v_height <- pop_v(x)
v_height

pop_sd <- function(x){sqrt(v)}
sd_height <- pop_sd(x)
sd_height
```

```{r}
n <- 1000
v <- rnorm(n,mu,sd_height)
hist(v)
qqnorm(v)
qqline(v)
```
Yes the distribution for height looks to be quite normal. 

now I will do weight

```{r}
weight_mean <- function(x){sum(weight)/1000}
mu_weight <- weight_mean(x)
mu_weight

pop_v <- function(x){sum((weight-mu_weight)^2)/(1000)}
v_weight <- pop_v(x)
v_weight

pop_sd <- function(x){sqrt(v_weight)}
sd_weight <- pop_sd(x)
sd_weight
```

```{r}
n <- 1000
v <- rnorm(n,mu_weight,sd_weight)
hist(v)
qqnorm(v)
qqline(v)
```

The distribution for weight also seems to look very normal as well.

Now I will do age.

```{r}
age <- (d$age)

age_mean <- function(x){sum(age)/1000}
mu_age <- age_mean(x)
mu_age

pop_v <- function(x){sum((age-mu_age)^2)/(1000)}
v_age <- pop_v(x)
v_age

pop_sd <- function(x){sqrt(v_age)}
sd_age <- pop_sd(x)
sd_age
```

```{r}
n <- 1000
v <- rnorm(n,mu_age,sd_age)
hist(v)
qqnorm(v)
qqline(v)
```
this also looks to be quite normal as nothing deviates from the line too much. 

```{r}
z_killed <- (d$zombies_killed)

z_killed_mean <- function(x){sum(z_killed)/1000}
mu_z_killed <- z_killed_mean(x)
mu_z_killed

pop_v <- function(x){sum((z_killed-mu_z_killed)^2)/(1000)}
v_z_killed <- pop_v(x)
v_z_killed

pop_sd <- function(x){sqrt(v_z_killed)}
sd_z_killed <- pop_sd(x)
sd_z_killed
```

```{r}
n <- 1000
v <- rnorm(n,mu_z_killed,sd_z_killed)
hist(v)
qqnorm(v)
qqline(v)
```

I will next do years of edu

```{r}
y_of_edu <- (d$years_of_education)

y_of_edu_mean <- function(x){sum(y_of_edu)/1000}
mu_y_of_edu <- y_of_edu_mean(x)
mu_y_of_edu

pop_v <- function(x){sum((y_of_edu-mu_y_of_edu)^2)/(1000)}
v_y_of_edu <- pop_v(x)
v_y_of_edu

pop_sd <- function(x){sqrt(v_y_of_edu)}
sd_y_of_edu <- pop_sd(x)
sd_y_of_edu
```

```{r}
n <- 1000
v <- rnorm(n,mu_y_of_edu,sd_y_of_edu)
hist(v)
qqnorm(v)
qqline(v)
```

I cannot find which one of these is not drawn from a normal distribution all of them seemed to be drawn from a normal distribution if I have done this correctly?

Question#5

Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal...

```{r}
k <- 1
n <- 30
s <- NULL

for (i in 1:k){
    s[[i]] <- sample(d,size=n, replace=FALSE)
}
```

the above did not work...

```{r}
mysample <- d[sample(1:nrow(d), 30,
   replace=FALSE),]
mysample
```

```{r}
table(mysample$height)
```

```{r}
mean(mysample$height)
sd(mysample$height)
```

Constucting the standard error for my sample height.

```{r}
pop_se <- sqrt(^2/n)
```

I am struggling to figure out how to do this, I have spent a long time on number 5 and cannot figure it out, I need some help. Something happened to my stnadard deviation from my population once I have removed the 30 variables and now I can not figure out what to do and I have run out of time. 

